---
title: "Runapp talk"
author: "James Goldie"
format:
  revealjs: 
    theme: [default, style.scss]
---

## Outline

- What is Quarto?
  - How it builds on RMarkdown
    - RMarkdown/Knitr ecosystem, extensions, other languages
    - Extensibility! 🎉
    - But also: fragmentation,which  and heavy reliance on R
  - Quarto packs all these tools in
    - Only needs R if you're doing computation with R
    - ...

## Slide 1: blah
```{r}
mydata <- data.frame(
  x = 1:10,
  y = (1:10)^2)

ojs_define(mydata)
```

```{ojs}
Reveal.on("stackslide", () => { console.log("Reached stackslide!"); } );
Reveal.on("fragmentshown", e => { 
  console.log("Reached fragment #" + e.fragment.attributes["data-fragment-index"].value);
  console.log(e);} );
```

A very quiet slide

## Slide 2: iframe background {auto-animate=true data-preload=true background-iframe="https://www.google.com/maps/embed?pb=!1m14!1m12!1m3!1d50379.12545547731!2d145.06408939156861!3d-37.89080691987292!2m3!1f0!2f0!3f0!3m2!1i1024!2i768!4f13.1!5e0!3m2!1sen!2sau!4v1649385361305!5m2!1sen!2sau"}

And something else!

## Slide 3: stack and "persistent" chart {data-state="stackslide"}

::: {.columns}

::: {.column width="60%"}
```{ojs}
someChart = Plot.barY(transpose(mydata), {x: "x", y: "y"}).plot({
  width: 600,
  height: 550,
  style: {
    background: "none",
    fontFamily: "Source Serif Pro",
    fontSize: 14
  }});
```
:::

::: {.column width="40%"}

::: {.r-stack}

::: {.fragment .fade-in-then-out data-fragment-index="1"}
Here's one point...
:::

::: {.fragment .fade-in-then-out data-fragment-index="2"}
And another...
:::

::: {.fragment .fade-in-then-out data-fragment-index="3"}
... And something else!
:::

:::
:::
:::

## Slide 4: some more stuff

A loud slide with an R chart on it!

```{r}
library(ggplot2)
ggplot(mydata) +
  aes(x, y) +
  geom_col() +
  theme_minimal() +
  theme(
    plot.background = element_blank()
  )
```

## Slide 5: big twist

Can this button affect state?

```{ojs}
viewof backButton = Inputs.button("Return to slide 1",
  {value: null, reduce: () => Reveal.slide(1) });
```

```{ojs}
state = Reveal.getState();
msg = html`You're currently on slide H: ${state.indexh}, V: ${state.indexV}, F: ${state.indexf}`
```

